---
title: "purpleaireda"
output:
  pdf_document: default
  html_document: default
date: "2024-02-19"
---

The following compares indoor and outdoor metrics between paired sensors. Data is a snapshot of all sensors in SLC area on January 30, 2024.

Paired sensors were determined using haversine distance for each indoor sensor's latitude and longitude to find the closest outdoor sensor. After filtering down to sensors with `position_rating` >= 3, there were 137 unique indoor sensors. Each indoor sensor was paired with its closest outdoor counterpart, resulting in 97 unique outdoor sensors (some overlap).

```{r package load, message=FALSE, echo=FALSE}
library(lmtest)
library(ggplot2)
library(data.table)
library(tidyverse)
library(stargazer)
```


```{r, echo=FALSE}
pa_eda <- read.csv("./slc_sensor_data_20240130.csv")
pa_eda <- data.table(pa_eda)
```

```{r, echo=FALSE}
paired_data <- read.csv("./indoor_outdoor_matched.csv")
```


```{r, echo=FALSE}
# Create scatterplot for pm1.0
ggplot(paired_data, aes(x = outdoor_pm1.0, y = indoor_pm1.0)) +
  geom_point() +
  labs(x = "Outdoor PM1.0", y = "Indoor PM1.0") +
  ggtitle("Scatterplot of Indoor PM1.0 vs Outdoor PM1.0")

# Create scatterplot for pm2.5
ggplot(paired_data, aes(x = outdoor_pm2.5, y = indoor_pm2.5)) +
  geom_point() +
  labs(x = "Outdoor PM2.5", y = "Indoor PM2.5") +
  ggtitle("Scatterplot of Indoor PM2.5 vs Outdoor PM2.5")

# Create scatterplot for pm10.0
ggplot(paired_data, aes(x = outdoor_pm10.0, y = indoor_pm10.0)) +
  geom_point() +
  labs(x = "Outdoor PM10.0", y = "Indoor PM10.0") +
  ggtitle("Scatterplot of Indoor PM10.0 vs Outdoor PM10.0")

# Create scatterplot for scattering_coefficient
ggplot(paired_data, aes(x = outdoor_scattering_coefficient, y = indoor_scattering_coefficient)) +
  geom_point() +
  labs(x = "Outdoor scattering_coefficient", y = "Indoor scattering_coefficient") +
  ggtitle("Scatterplot of Indoor scattering_coefficient vs Outdoor scattering_coefficient")

# Create scatterplot for deciviews
ggplot(paired_data, aes(x = outdoor_deciviews, y = indoor_deciviews)) +
  geom_point() +
  labs(x = "Outdoor deciviews", y = "Indoor deciviews") +
  ggtitle("Scatterplot of Indoor deciviews vs Outdoor deciviews")

# Create scatterplot for visual_range
ggplot(paired_data, aes(x = outdoor_visual_range, y = indoor_visual_range)) +
  geom_point() +
  labs(x = "Outdoor visual_range", y = "Indoor visual_range") +
  ggtitle("Scatterplot of Indoor visual_range vs Outdoor visual_range")

# Create scatterplot for pressure
ggplot(paired_data, aes(x = outdoor_pressure, y = indoor_pressure)) +
  geom_point() +
  labs(x = "Outdoor pressure", y = "Indoor pressure") +
  ggtitle("Scatterplot of Indoor pressure vs Outdoor pressure")

# Create scatterplot for temperature
ggplot(paired_data, aes(x = outdoor_temperature, y = indoor_temperature)) +
  geom_point() +
  labs(x = "Outdoor temperature", y = "Indoor temperature") +
  ggtitle("Scatterplot of Indoor temperature vs Outdoor temperature")

# Create scatterplot for altitude
ggplot(paired_data, aes(x = outdoor_altitude, y = indoor_altitude)) +
  geom_point() +
  labs(x = "Outdoor altitude", y = "Indoor altitude") +
  ggtitle("Scatterplot of Indoor altitude vs Outdoor altitude")

# Create scatterplot for humidity
ggplot(paired_data, aes(x = outdoor_humidity, y = indoor_humidity)) +
  geom_point() +
  labs(x = "Outdoor humidity", y = "Indoor humidity") +
  ggtitle("Scatterplot of Indoor humidity vs Outdoor humidity")

```

```{r, echo=FALSE}
# Run a regression for pm1.0
pm1_lm_model <- lm(indoor_pm1.0 ~ outdoor_pm1.0, data = paired_data)

# Run a regression for pm2.5
pm2_5_lm_model <- lm(indoor_pm2.5 ~ outdoor_pm2.5, data = paired_data)

# Run a regression for pm10.0
pm10_lm_model <- lm(indoor_pm10.0 ~ outdoor_pm10.0, data = paired_data)

# Run a regression for scattering_coefficient
scattering_coefficient_lm_model <- lm(indoor_scattering_coefficient ~ outdoor_scattering_coefficient, data = paired_data)

# Run a regression for deciviews
deciviews_lm_model <- lm(indoor_deciviews ~ outdoor_deciviews, data = paired_data)

# Run a regression for visual_range
visual_range_lm_model <- lm(indoor_visual_range ~ outdoor_visual_range, data = paired_data)

# Run a regression for pressure
pressure_lm_model <- lm(indoor_pressure ~ outdoor_pressure, data = paired_data)

# Run a regression for temperature
temperature_lm_model <- lm(indoor_temperature ~ outdoor_temperature, data = paired_data)

# Run a regression for humidity
humidity_lm_model <- lm(indoor_humidity ~ outdoor_humidity, data = paired_data)

```

```{r, results='asis', echo=FALSE, warning=FALSE, message=FALSE}
stargazer(pm1_lm_model,
          pm2_5_lm_model,
          pm10_lm_model,
          title = 'Particulate Matter Variables',
          type = 'latex')
```

```{r, results='asis',  echo=FALSE, warning=FALSE, message=FALSE}
stargazer(scattering_coefficient_lm_model,
          deciviews_lm_model,
          visual_range_lm_model,
          title = 'Visibility-related Variables',
          type = 'latex')
```

```{r, results='asis',  echo=FALSE, warning=FALSE, message=FALSE}
stargazer(pressure_lm_model,
          temperature_lm_model,
          humidity_lm_model,
          title = 'Weather-related Variables',
          type = 'latex')
```